A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-10-04 sections/methodology/main.tex
Mention additional learning algorithms
- Add a sentence for fictitious play and stochastic fictitious play
- Reference the book: Thoery of learning in games
Cite Brent's bisection algorithm

The values of \(p_A\) and \(p_B\) that satisfy equation 
(\ref{eq:obj_distributor_1_1}) can be found by using Brent's bisection 
algorithm.
% TODO: Cite Brent's algorithm
The calculated value of \(p_A\) corresponds to the entry on the first row and 
first column of the routing matrix:

@@

>>>>

The values of \(p_A\) and \(p_B\) that satisfy equation 
(\ref{eq:obj_distributor_1_1}) can be found by using Brent's bisection 
algorithm~\cite{brent1973algorithms}.
The calculated value of \(p_A\) corresponds to the entry on the first row and 
first column of the routing matrix:

@@

In addition to asymmetric replicator dynamics, the learning algorithms
fictitious play and stochastic fictitious play \cite{fudenberg1998theory}
were used.
